---
title: "Correlation Analysis"
author: "William Sheppard"
date: "14/02/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(plyr)
library(tidyverse)
library(Hmisc)
library(corrplot)
library(ggpubr)
library(grid)
library(knitr)
library(kableExtra)

setwd("C:/Users/wills/Documents/Cataract/Analysis/cataract")

source("CorrelationAnalysis.R")
```

# Experiment 1

Change in all visual and task outcomes were calculated between visual conditions i.e. both vs worse, both versus better, better versus worse. 
All variables were subject to a Spearman's rank correlation, results are displayed below in *Fig X*. 
No variables showed marginal significance. 
Intercorrelations between motor measures are not reported here.
Spearman's correlation was choosen as these data were not normally distributed.

```{r e1Cor}

# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}

exp1_flat_matrix <- flattenCorrMatrix(exp1_change_cor$r, exp1_change_cor$P)
exp1_sig_cor <- exp1_flat_matrix[c(4, 11, 22),] 
  
write.csv(exp1_sig_cor, "C:/Users/wills/Documents/Cataract/Figures/Correlation/exp1_cor.csv")

kable(exp1_sig_cor, caption = "Spearman's Correlation Matrix", digits = 3, col.names = c("", "", "*r~s~*", "*p*"))
#show(cor1)

```

A higher LogMAR value is indicative that the change to visual condition has made VA worse.
Results of the Spearman correlation indicated that there was a significant positive association between increasing LogMAR scores and increased Tracking RMSE with no guide at fast speed (*rs*(211) = .17, *p* = .012), and with a guide at medium speed (*rs*(211) = .16, *p* = .021).

```{r e1TrackingNGPlot}
exp1_change_VA_trackingNG
```

```{r e1TrackingWGPlot}
exp1_change_VA_trackingWG
```

The Spearman's correlation also indicated that there was a significant positive association between increasing LogMAR scores and movememnt time (s) in the aiming task (*rs*(211) = .15, *p* = .034).

```{r e1AimingPlot}
exp1_change_VA_aiming
```

# Experiment 2

All significant, or marginally significant results of a Spearman's correlation are displayed below in *Fig X*.
Intercorrelations between motor measures are not reported here.

```{r e2Cor}
exp2_flat_matrix <- flattenCorrMatrix(AC_cor$r, AC_cor$P)
exp2_sig_cor <- exp2_flat_matrix[c(18),]
exp2_marg_sig <- exp2_flat_matrix[c(5, 9, 16),]
  
write.csv(exp2_marg_sig, "C:/Users/wills/Documents/Cataract/Figures/Correlation/exp2_cor.csv")

kable(exp2_sig_cor, caption = "Spearman's Correlation Matrix", digits = 3, col.names = c("", "", "*r~s~*", "*p*"))

```

A negative value for stereoacuity indicates that the manipulation has made stereoacuity worse, where as a higher value for change to pouring time is indicative of worse performance i.e. the particiapnt has taken longer to complete the task.
The Spearman's correlation also indicated that there was a significant negative association between change in stereoacuity scores and pouring time (s) in the aiming task (*rs*(88) = -.21, *p* = .043)
```{r e2Plots}

exp2_change_stereo_pouringtime

```
