---
title: "Visual Measures Check - Cataract Exp 1"
author: "William Sheppard"
date: "21/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
```

Rigmoor added a comment to the paper that got me thinking:
Participants were aged 18 – 23 years old (mean = 19.37, SD = 1.22), five participants were left-handed. Participants were required to be 18 years old or over and have normal or corrected-to-normal eyesight (**logMAR <= 0.00?**).

This got me thinking - do any of our participants have particularly poor 

```{r import dataset}
setwd("C:/Users/wills/Documents/Cataract/Data")
all_data <- read.csv("AllData_forJASP.csv")
```


# Summary of No Filter (baseline) VA data
One sample t-test - Is the data sig. different from 0?
From these tests we can infer:
  Baseline VA data was normally distributed in this sample and did not significantly differ from zero
```{r VA}
VA_sum <- summary(all_data$VA_NoFilter)
VA_upper_bound <- sd(all_data$VA_NoFilter)

show(VA_sum)
show(VA_upper_bound)
```

## Did any participants have baseline VA sig. greater than 0?
```{r Over zero}
high_VA <- all_data %>%
  filter(VA_NoFilter > VA_upper_bound)

```
Participants with baseline VA greater than `r round(VA_upper_bound, digits = 3)` cannot be considered as having normal/corrected to normal vision,
this would suggest that particiapnts: `r  high_VA$P_ID` have a VA sig. greater than 0, and should be included in our results?

# Summary of No Filter (baseline) Stereoacuity data

```{r Stereo}
Stereo_sum <- summary(all_data$Stereo_NoFilter)


show(Stereo_sum)


low_stereo <- all_data %>%
  filter(Stereo_NoFilter < 4)
```
Individuals who score 3 or less on the Wirt circles test are considered stereoblind (stereoacuity worse than 140 seconds of arc),

Our data would suggest that participants: `r low_stereo$P_ID` meet the criteria for stereoblindness and it may not be appropriate to include them in further anaysis


# Summary of No Filter (baseline) CS data
```{r CS}
CS_sum <- summary(all_data$CS_NoFilter)


show(CS_sum)


```
Normal range of CS scores = 12-14
Small range of results, therefore no participants will be excluded based on their CS scores

```{r}
PP_exclude <- unique(c(high_VA$P_ID, low_stereo$P_ID))
#show(PP_exclude)
```
Therefore, participants `r PP_exclude` baseline scores cannot be considered representitive and may there need to be removed from further analysis.