---
title: "exp2_IntOccDiff"
author: "William Sheppard"
date: "29/05/2020"
output:
  html_document: default
  pdf_document: default
---
# This script investigates the effect of removing participants with no interocular difference or large interocular difference on CKAT measures

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(root.dir = "C:/Users/wills/Documents/Cataract/Data")
library(tidyverse)
library(ggpubr)
library(rstatix)
```

```{r import data}
# import data
all_data <- read.csv("C:/Users/wills/Documents/Cataract/Data/exp1_wide_ALL_MEASURES.csv") 

# Filter participants with no IOdiff
nodiff_data <- all_data %>%
  filter(LogMAR_EyeDifference != 0)

bigdiff_data <- all_data %>%
  filter(LogMAR_EyeDifference <= 0.2)

diff_data <- all_data %>%
  filter(LogMAR_EyeDifference > 0.2)
```
data: data frame
dv: (numeric) the dependent (or outcome) variable name.
wid: variable name specifying the case/sample identifier.
within: within-subjects factor or grouping variable


# Aiming
One-way repeated measures anova
dv = MT
wid = P_ID_
within = visual condition

## All data
```{r Aiming all data}
aiming_data <- all_data %>%
  select(P_ID_, Aiming_Worse:Aiming_Better) %>%
  rename("Worse" = "Aiming_Worse",
         "Better" = "Aiming_Better",
         "Both" = "Aiming_Both")

# gather columns to long format
aiming_data <- aiming_data %>%
  gather(key = "eye_condition", value = "MT", Worse, Both, Better) %>%
  convert_as_factor(P_ID_, eye_condition) %>%
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

# Get summary statistics
aiming_summary_stats <- aiming_data %>%
  group_by(eye_condition) %>%
  get_summary_stats(MT, type = "mean_sd")
#aiming_summary_stats

# Group boxplot
aiming_bp <- ggplot(aiming_data, aes(x = eye_condition, y = MT)) +
  geom_boxplot() 
aiming_bp

aiming_qq <- ggqqplot(aiming_data, "MT", facet.by = "eye_condition") # happy that data is normally distributed

# Run ANOVA
aiming.aov <- anova_test(data = aiming_data, 
                         dv = MT, 
                         wid = P_ID_, 
                         within = eye_condition,
                         effect.size = "pes")
get_anova_table(aiming.aov)

# pairwise comparison
aiming_pwc <- aiming_data %>%
  pairwise_t_test(
    MT ~ eye_condition, paired = TRUE,
    p.adjust.method = "holm"
  )
aiming_pwc

aiming_cohens_d <- aiming_data %>%
  cohens_d(MT ~ eye_condition, paired = TRUE)
aiming_cohens_d
```

## Aiming - Interoccular difference == 0.0 logMAR removed
results are almost exactly the same as including all data!
Effect sizes are slightly smaller after excluding data.
```{r Aiming NoDiff data}
aiming_nodiff <- nodiff_data %>%
  select(P_ID_, Aiming_Worse:Aiming_Better) %>%
  rename("Worse" = "Aiming_Worse",
         "Better" = "Aiming_Better",
         "Both" = "Aiming_Both")

# gather columns to long format
aiming_nodiff <- aiming_nodiff %>%
  gather(key = "eye_condition", value = "MT", Worse, Both, Better) %>%
  convert_as_factor(P_ID_, eye_condition) %>%
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

# Get summary statistics
aiming_nodiff_summary_stats <- aiming_nodiff %>%
  group_by(eye_condition) %>%
  get_summary_stats(MT, type = "mean_sd")
#aiming_nodiff_summary_stats

# Group boxplot
aiming_nodiff_bp <- ggplot(aiming_nodiff, aes(x = eye_condition, y = MT)) +
  geom_boxplot() 
aiming_nodiff_bp

aiming_nodiff_qq <- ggqqplot(aiming_nodiff, "MT", facet.by = "eye_condition") # happy that data is normally distributed

# Run ANOVA
aiming_nodiff.aov <- anova_test(data = aiming_nodiff, 
                         dv = MT, 
                         wid = P_ID_, 
                         within = eye_condition,
                         effect.size = "pes")
get_anova_table(aiming_nodiff.aov)

# pairwise comparison
aiming_nodiff_pwc <- aiming_nodiff %>%
  pairwise_t_test(
    MT ~ eye_condition, paired = TRUE,
    p.adjust.method = "holm"
  )
aiming_nodiff_pwc

aiming_nodiff_cohens_d <- aiming_nodiff %>%
  cohens_d(MT ~ eye_condition, paired = TRUE)
aiming_nodiff_cohens_d
```


## Aiming - Interoccular difference > 0.2 logMAR removed
Compared to all data, effect size of better v both has increase from 0.44 to 0.51.
Otherwise, results are largely the same.
```{r Aiming BigDiff data}
aiming_bigdiff <- bigdiff_data %>%
  select(P_ID_, Aiming_Worse:Aiming_Better) %>%
  rename("Worse" = "Aiming_Worse",
         "Better" = "Aiming_Better",
         "Both" = "Aiming_Both")

# gather columns to long format
aiming_bigdiff <- aiming_bigdiff %>%
  gather(key = "eye_condition", value = "MT", Worse, Both, Better) %>%
  convert_as_factor(P_ID_, eye_condition) %>%
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

# Get summary statistics
aiming_bigdiff_summary_stats <- aiming_bigdiff %>%
  group_by(eye_condition) %>%
  get_summary_stats(MT, type = "mean_sd")
aiming_bigdiff_summary_stats

# Group boxplot
aiming_bigdiff_bp <- ggplot(aiming_bigdiff, aes(x = eye_condition, y = MT)) +
  geom_boxplot() 
aiming_bigdiff_bp


aiming_bigdiff_qq <- ggqqplot(aiming_bigdiff, "MT", facet.by = "eye_condition") # happy that data is normally distributed

# Run ANOVA
aiming_bigdiff.aov <- anova_test(data = aiming_bigdiff, 
                         dv = MT, 
                         wid = P_ID_, 
                         within = eye_condition,
                         effect.size = "pes")
get_anova_table(aiming_bigdiff.aov)

# pairwise comparison
aiming_bigdiff_pwc <- aiming_bigdiff %>%
  pairwise_t_test(
    MT ~ eye_condition, paired = TRUE,
    p.adjust.method = "holm"
  )
aiming_bigdiff_pwc

aiming_bigdiff_cohens_d <- aiming_bigdiff %>%
  cohens_d(MT ~ eye_condition, paired = TRUE)
aiming_bigdiff_cohens_d
```

## Aiming - Interoccular difference < 0.2 logMAR removed
No significant main effect of vision.
Sample size is now much smaller - may exlain the lack of effect (N = 11)
```{r Aiming Diff data}
aiming_diff <- diff_data %>%
  select(P_ID_, Aiming_Worse:Aiming_Better) %>%
  rename("Worse" = "Aiming_Worse",
         "Better" = "Aiming_Better",
         "Both" = "Aiming_Both")

# gather columns to long format
aiming_diff <- aiming_diff %>%
  gather(key = "eye_condition", value = "MT", Worse, Both, Better) %>%
  convert_as_factor(P_ID_, eye_condition) %>%
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

# Get summary statistics
aiming_diff_summary_stats <- aiming_diff %>%
  group_by(eye_condition) %>%
  get_summary_stats(MT, type = "mean_sd")
#aiming_diff_summary_stats

# Group boxplot
aiming_diff_bp <- ggplot(aiming_diff, aes(x = eye_condition, y = MT)) +
  geom_boxplot() 
aiming_diff_bp


aiming_diff_qq <- ggqqplot(aiming_diff, "MT", facet.by = "eye_condition") # happy that data is normally distributed
#aiming_diff_qq

# Run ANOVA
aiming_diff.aov <- anova_test(data = aiming_diff, 
                         dv = MT, 
                         wid = P_ID_, 
                         within = eye_condition,
                         effect.size = "pes")
get_anova_table(aiming_diff.aov)
```

# Steering
## Two-way repeated measures anova
dv = pPA
wid = P_ID_
within = visual condition, shape

It appears that steering dat ais non-normally distributed for some conditions shape A - Worse and Better, shape B - Worse 
All same results, i got different values for cohens d:
better vs both = 0.28
worse vs both = 0.33
```{r Steering all data}
steering_data <- all_data %>%
  select(P_ID_, SteeringA_Worse:SteeringB_Both) %>%
  rename("A_Worse" = "SteeringA_Worse",
         "A_Better" = "SteeringA_Better",
         "A_Both" = "SteeringA_Both",
         "B_Worse" = "SteeringB_Worse",
         "B_Better" = "SteeringB_Better",
         "B_Both" = "SteeringB_Both")

# gather columns to long format
steering_data <- steering_data %>%
  gather(key = "condition", value = "pPA", A_Worse, A_Better, A_Both, B_Worse, B_Better, B_Both) %>%
  extract(condition, c("shape", "eye_condition"), "([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

steering_summary_stats <- steering_data %>%
  group_by(shape, eye_condition) %>%
  get_summary_stats(pPA, type = "mean_sd")
#steering_summary_stats

steering_bp <- ggplot(steering_data, aes(x = eye_condition, y = pPA, color = shape)) + 
  geom_boxplot()
steering_bp

steering_qq <- ggqqplot(steering_data, "pPA", ggtheme = theme_bw()) +
  facet_grid(eye_condition ~ shape, labeller = "label_both")
steering_qq

steering.aov <- anova_test(
  data = steering_data,
  dv = pPA,
  wid = P_ID_,
  within = c(eye_condition, shape),
  effect.size = "pes"
)
get_anova_table(steering.aov)

steering_pwc_eye <- steering_data %>%
  pairwise_t_test(
    pPA ~ eye_condition, paired = TRUE, 
    p.adjust.method = "holm"
    )
steering_pwc_eye

steering_cohens_d <- steering_data %>%
  cohens_d(pPA ~ eye_condition, paired = TRUE)
steering_cohens_d
```

## Steering - Interoccular difference == 0.0 logMAR removed
It appears that steering dat ais non-normally distributed for some conditions shape A - Worse and Better, shape B - Worse 
compared to all data, effect size of better v both has increased from 0.28 to 0.34
```{r Steering NoDiff}
steering_nodiff <- nodiff_data %>%
  select(P_ID_, SteeringA_Worse:SteeringB_Both) %>%
  rename("A_Worse" = "SteeringA_Worse",
         "A_Better" = "SteeringA_Better",
         "A_Both" = "SteeringA_Both",
         "B_Worse" = "SteeringB_Worse",
         "B_Better" = "SteeringB_Better",
         "B_Both" = "SteeringB_Both")

# gather columns to long format
steering_nodiff <- steering_nodiff %>%
  gather(key = "condition", value = "pPA", A_Worse, A_Better, A_Both, B_Worse, B_Better, B_Both) %>%
  extract(condition, c("shape", "eye_condition"), "([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

steering_nodiff_summary_stats <- steering_nodiff %>%
  group_by(shape, eye_condition) %>%
  get_summary_stats(pPA, type = "mean_sd")
#steering_nodiff_summary_stats

steering_nodiff_bp <- ggplot(steering_nodiff, aes(x = eye_condition, y = pPA, color = shape)) + 
  geom_boxplot()
steering_nodiff_bp

steering_nodiff_qq <- ggqqplot(steering_nodiff, "pPA", ggtheme = theme_bw()) +
  facet_grid(eye_condition ~ shape, labeller = "label_both")
steering_nodiff_qq

steering_nodiff.aov <- anova_test(
  data = steering_nodiff,
  dv = pPA,
  wid = P_ID_,
  within = c(eye_condition, shape),
  effect.size = "pes"
)
get_anova_table(steering_nodiff.aov)

steering_nodiff_pwc_eye <- steering_nodiff %>%
  pairwise_t_test(
    pPA ~ eye_condition, paired = TRUE, 
    p.adjust.method = "holm"
    )
steering_nodiff_pwc_eye

steering_nodiff_cohens_d <- steering_nodiff %>%
  cohens_d(pPA ~ eye_condition, paired = TRUE)
steering_nodiff_cohens_d
```

## Steering - Interoccular difference > 0.2 logMAR removed
It appears that steering data is non-normally distributed for some conditions shape A - Worse and Better, shape B - Worse
compared to all data, effect size of better v both has increased from 0.28 to 0.33 and worse v both reduced from .33 to .32
```{r Steering BigDiff}
steering_bigdiff <- bigdiff_data %>%
  select(P_ID_, SteeringA_Worse:SteeringB_Both) %>%
  rename("A_Worse" = "SteeringA_Worse",
         "A_Better" = "SteeringA_Better",
         "A_Both" = "SteeringA_Both",
         "B_Worse" = "SteeringB_Worse",
         "B_Better" = "SteeringB_Better",
         "B_Both" = "SteeringB_Both")

# gather columns to long format
steering_bigdiff <- steering_bigdiff %>%
  gather(key = "condition", value = "pPA", A_Worse, A_Better, A_Both, B_Worse, B_Better, B_Both) %>%
  extract(condition, c("shape", "eye_condition"), "([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

steering_bigdiff_summary_stats <- steering_bigdiff %>%
  group_by(shape, eye_condition) %>%
  get_summary_stats(pPA, type = "mean_sd")
steering_bigdiff_summary_stats

steering_bigdiff_bp <- ggplot(steering_bigdiff, aes(x = eye_condition, y = pPA, color = shape)) + 
  geom_boxplot()
steering_bigdiff_bp

steering_bigdiff_qq <- ggqqplot(steering_bigdiff, "pPA", ggtheme = theme_bw()) +
  facet_grid(eye_condition ~ shape, labeller = "label_both")
steering_bigdiff_qq

steering_bigdiff.aov <- anova_test(
  data = steering_bigdiff,
  dv = pPA,
  wid = P_ID_,
  within = c(eye_condition, shape),
  effect.size = "pes"
)
get_anova_table(steering_bigdiff.aov)

steering_bigdiff_pwc_eye <- steering_bigdiff %>%
  pairwise_t_test(
    pPA ~ eye_condition, paired = TRUE, 
    p.adjust.method = "holm"
    )
steering_bigdiff_pwc_eye

steering_bigdiff_cohens_d <- steering_bigdiff %>%
  cohens_d(pPA ~ eye_condition, paired = TRUE)
steering_bigdiff_cohens_d
```


## Steering - Interoccular difference < 0.2 logMAR removed
No main effect of vision
```{r Steering Diff}
steering_diff <- diff_data %>%
  select(P_ID_, SteeringA_Worse:SteeringB_Both) %>%
  rename("A_Worse" = "SteeringA_Worse",
         "A_Better" = "SteeringA_Better",
         "A_Both" = "SteeringA_Both",
         "B_Worse" = "SteeringB_Worse",
         "B_Better" = "SteeringB_Better",
         "B_Both" = "SteeringB_Both")

# gather columns to long format
steering_diff <- steering_diff %>%
  gather(key = "condition", value = "pPA", A_Worse, A_Better, A_Both, B_Worse, B_Better, B_Both) %>%
  extract(condition, c("shape", "eye_condition"), "([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both"))

steering_diff_summary_stats <- steering_diff %>%
  group_by(shape, eye_condition) %>%
  get_summary_stats(pPA, type = "mean_sd")
#steering_diff_summary_stats

steering_diff_bp <- ggplot(steering_diff, aes(x = eye_condition, y = pPA, color = shape)) + 
  geom_boxplot()
steering_diff_bp

steering_diff_qq <- ggqqplot(steering_diff, "pPA", ggtheme = theme_bw()) +
  facet_grid(eye_condition ~ shape, labeller = "label_both")
steering_diff_qq

steering_diff.aov <- anova_test(
  data = steering_diff,
  dv = pPA,
  wid = P_ID_,
  within = c(eye_condition, shape),
  effect.size = "pes"
)
get_anova_table(steering_diff.aov)
```

# Tracking
## Three-way repeated measures anova
dv = RMSE
wid = P_ID_
within = visual condition, speed, guide

Some conditions are not normally distributed, see qq plot for details

No main effect of eye condition.
Main effect of guide and speed, and a sig. guide*speed interaction.
Not interested in this effect in this paper, therefore, I am not probing this any further.
```{r Tracking all data}
tracking_data <- all_data %>%
  select(P_ID_, Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both)%>%
  filter(P_ID_ != 44) 

# gather columns to long format
tracking_data <- tracking_data %>%
  gather(key = "condition", value = "RMSE", Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both) %>%
  extract(condition, c("guide", "speed", "eye_condition"), "([[:alnum:]]+[[:punct:]]+[[:alnum:]]+)_([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, guide, speed, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both")) 

tracking_data$RMSE <- as.numeric(tracking_data$RMSE)

tracking_summary_stats <- tracking_data %>%
  group_by(guide, speed, eye_condition) %>%
  get_summary_stats(RMSE, type = "mean_sd")
#tracking_summary_stats

tracking_bp <- ggplot(tracking_data, aes(x = eye_condition, y = RMSE, color = speed)) + 
  geom_boxplot() +
  facet_grid(guide~.)
tracking_bp

tracking_qq <- ggqqplot(tracking_data, "RMSE", ggtheme = theme_bw()) +
  facet_grid(speed + guide ~ eye_condition, labeller = "label_both")
tracking_qq

tracking.aov <- anova_test(
  data = tracking_data,
  dv = RMSE,
  wid = P_ID_,
  within = c(eye_condition, speed, guide),
  effect.size = "pes"
)
get_anova_table(tracking.aov)
```

## Tracking - Interoccular difference == 0.0 logMAR removed

Some conditions are not normally distributed, see qq plot for details

No main effect of eye condition.
Main effect of guide and speed, and a sig. guide*speed interaction.
Not interested in this effect in this paper, therefore, I am not probing this any further.
```{r Tracking NoDiff}
tracking_nodiff <- nodiff_data %>%
  select(P_ID_, Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both)%>%
  filter(P_ID_ != 44) 

# gather columns to long format
tracking_nodiff <- tracking_nodiff %>%
  gather(key = "condition", value = "RMSE", Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both) %>%
  extract(condition, c("guide", "speed", "eye_condition"), "([[:alnum:]]+[[:punct:]]+[[:alnum:]]+)_([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, guide, speed, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both")) 

tracking_nodiff$RMSE <- as.numeric(tracking_nodiff$RMSE)

tracking_nodiff_summary_stats <- tracking_nodiff %>%
  group_by(guide, speed, eye_condition) %>%
  get_summary_stats(RMSE, type = "mean_sd")
#tracking_nodiff_summary_stats

tracking_nodiff_bp <- ggplot(tracking_nodiff, aes(x = eye_condition, y = RMSE, color = speed)) + 
  geom_boxplot() +
  facet_grid(guide~.)
tracking_nodiff_bp

tracking_nodiff_qq <- ggqqplot(tracking_nodiff, "RMSE", ggtheme = theme_bw()) +
  facet_grid(speed + guide ~ eye_condition, labeller = "label_both")
tracking_nodiff_qq

tracking_nodiff.aov <- anova_test(
  data = tracking_nodiff,
  dv = RMSE,
  wid = P_ID_,
  within = c(eye_condition, speed, guide),
  effect.size = "pes"
)
get_anova_table(tracking_nodiff.aov)
```

## Tracking - Interoccular difference > 0.2 logMAR removed

Some conditions are not normally distributed, see qq plot for details

No main effect of eye condition.
Main effect of guide and speed, and a sig. guide*speed interaction.

Main effect of eye condition approaching sig. (p = .066)
pair wise comparisons indicate a significant diference between worse and both, but the efect size is negligable (d = 0.15)
```{r Tracking BigDiff}
tracking_bigdiff <- bigdiff_data %>%
  select(P_ID_, Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both)%>%
  filter(P_ID_ != 44) 

# gather columns to long format
tracking_bigdiff <- tracking_bigdiff %>%
  gather(key = "condition", value = "RMSE", Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both) %>%
  extract(condition, c("guide", "speed", "eye_condition"), "([[:alnum:]]+[[:punct:]]+[[:alnum:]]+)_([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, guide, speed, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both")) 

tracking_bigdiff$RMSE <- as.numeric(tracking_bigdiff$RMSE)

tracking_bigdiff_summary_stats <- tracking_bigdiff %>%
  group_by(guide, speed, eye_condition) %>%
  get_summary_stats(RMSE, type = "mean_sd")
tracking_bigdiff_summary_stats

tracking_bigdiff_bp <- ggplot(tracking_bigdiff, aes(x = eye_condition, y = RMSE, color = speed)) + 
  geom_boxplot() +
  facet_grid(guide~.)
tracking_bigdiff_bp

tracking_bigdiff_qq <- ggqqplot(tracking_bigdiff, "RMSE", ggtheme = theme_bw()) +
  facet_grid(speed + guide ~ eye_condition, labeller = "label_both")
tracking_bigdiff_qq

tracking_bigdiff.aov <- anova_test(
  data = tracking_bigdiff,
  dv = RMSE,
  wid = P_ID_,
  within = c(eye_condition, speed, guide),
  effect.size = "pes"
)
get_anova_table(tracking_bigdiff.aov)

tracking_bigdiff_pwc_eye <- tracking_bigdiff %>%
  pairwise_t_test(
    RMSE ~ eye_condition, paired = TRUE, 
    p.adjust.method = "holm"
    )
tracking_bigdiff_pwc_eye

tracking_bigdiff_cohens_d <- tracking_bigdiff %>%
  cohens_d(RMSE ~ eye_condition, paired = TRUE)
tracking_bigdiff_cohens_d
```

## Tracking - Interoccular difference < 0.2 logMAR removed

WG-Fast-Both - has a really high mean RMSE (~24) - Participant 116 has error of 103.74 for this condition

main effect of speed only
```{r Tracking Diff}
tracking_diff <- diff_data %>%
  select(P_ID_, Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both)%>%
  filter(P_ID_ != 44) 

# gather columns to long format
tracking_diff <- tracking_diff %>%
  gather(key = "condition", value = "RMSE", Trkng_NG_Slow_Worse:Trkng_WG_Fast_Both) %>%
  extract(condition, c("guide", "speed", "eye_condition"), "([[:alnum:]]+[[:punct:]]+[[:alnum:]]+)_([[:alnum:]]+)_([[:alnum:]]+)") %>%
  convert_as_factor(P_ID_, guide, speed, eye_condition) %>% 
  reorder_levels(eye_condition, order = c("Worse", "Better", "Both")) 

tracking_diff$RMSE <- as.numeric(tracking_diff$RMSE)

tracking_diff_summary_stats <- tracking_diff %>%
  group_by(guide, speed, eye_condition) %>%
  get_summary_stats(RMSE, type = "mean_sd")
#tracking_diff_summary_stats

tracking_diff_bp <- ggplot(tracking_diff, aes(x = eye_condition, y = RMSE, color = speed)) + 
  geom_boxplot() +
  facet_grid(guide~.)
tracking_diff_bp

tracking_diff_qq <- ggqqplot(tracking_diff, "RMSE", ggtheme = theme_bw()) +
  facet_grid(speed + guide ~ eye_condition, labeller = "label_both")
tracking_diff_qq

tracking_diff.aov <- anova_test(
  data = tracking_diff,
  dv = RMSE,
  wid = P_ID_,
  within = c(eye_condition, speed, guide),
  effect.size = "pes"
)
get_anova_table(tracking_diff.aov)
```